Tidal field anisotropy as a tracer of cosmic voids

### 2015-01-23 cosmic_voids.tex
Velocity profiles analysis, done

>>>>

All the profiles behave linearly near to the void centres, where larger 
voids display more steep slopes. This indicates larger voids are being
pulled out more strongly by nearby structures. On the other hand, at 
large radius, all the profiles decrease to the zero background velocity,
where larger voids reach this value first as their outer radial layers 
average a large portion of volume.

Like the density, these results also point out to an universal radial 
velocity profiles of voids \citep{Hamaus14}.
